\section{Sloped Trend Lines}

\quad Sloped trend lines in technical analysis are commonly defined as sloped lines
that touch a high or low candle at least 3 times and all candles the line covers
are at least less than or equal or greater than or equal to the values of the
line. Below is an example of the resistance line with $s(x)$ representing a
theoretical stock price chart and $t(x)$ represents a theoretical trend line.

\begin{center}
  \begin{tikzpicture}
    \begin{axis}[
        grid = major,
        xmin = 0,
        xmax = 10,
        ymin = 0,
        ymax = 10,
        xlabel = {time},
        ylabel = {price},
    ]
      \addplot[
        color = black,
        domain = 0:10,
      ]{-((x-4.1) + sin(deg(4*x))) + 6};
      \legend{$s(x)$,$t(x)$}
      \addplot[
        color = blue,
        domain = 0:10
      ]{-x + 11.1};
    \end{axis}
  \end{tikzpicture}
\end{center}

It is easy to see in the domain $[0,10]$ that $s(x) \le t(x)$. There is another
feature that is not so clear, and that is that each confirmation is exactly
the same same width away from each other. Simply finding a line with $3$
confirmations is not enough to provide a valid trend line, instead $3$
confirmations are needed as well as symmetry between each confirmation.
Problems arise when going from theory to actuality in the fact that in reality
there is almost never a trend line that has these two properties, instead
we must approximate or quantify how good the real trend is to its
theoretical counterpart. We propose two arguments, Orbital Symmetry and
Trend Area in finding these lines.

\subsection{Orbital Symmetry}
\quad Orbital Symmetry is a proposed technique to find well symmetric trend
lines. The question is simple, given a list of candles high, lows, close, or
open denoted by the ordered set

\[
  S = \{
    C_{0}, C_{1}, ... C_{n-1} \text{\space} |
    \text{\space} n \in \mathbb{Z}
  \}
\] does $S$ satisfy the
conditions of an orbitally symmetric trend line?
We will define an Orbitally Symmetric trend line as a trend lines with
symmetric points around a circle. For example, if the perfect point of symmetry
is at point $n$, then any point between $[n-\frac{w}{2}, n+\frac{w}{2}] w
\in \mathbb{Z}$ can be
considered a perfect point of symmetry. Below is a conjecture that the given
set $S$ satisfies an orbitally symmetric trend line.

\begin{proof}[Conjecture: Orbitally Symmetric Trend Line]
  An order set
  $$
    S = \{C_{0}, C_{1}, ... C_{n-1} \text{\space} | \text{\space} n \in \mathbb{Z}\}
  $$ with $|S| = n$,a valid orbitally symmetric trend line iff
  $|S| \ge 3$ and there exists a line $f(n)$ constructed by the points
  $(0, C_{0})$ $(n-1,C_{n-1})$ such that
  \[
    (\forall x \in S, x \le f(x)) \lor (\forall x \in S, x \ge f(x))
  \]
  and
  \[
    \exists w|n
  \]
  \[
    \forall c \equiv w \pmod n
  \]
  \[
    \exists x \in [c-\frac{w}{2}, c+\frac{w}{2})] : x = f(x)
  \]
\end{proof}


\subsection{Trend Area}


